Preprocess

### 2024-01-17 manuscript/manuscript.tex
Checking counts

\title[Determining Causes of Death with ChatGPT: A Case Study of Verbal Autopsy Data in Sierra Leone from 2019-2022]{Determining Causes of Death with ChatGPT: A Case Study of Verbal Autopsy Data in Sierra Leone from 2019-2022}

@@

In 2019, 41 million people die prematurely from noncommunicable diseases every year, accounting for 74\% of all deaths globally \cite{worldhealthorganizationNonCommunicableDiseases2019}. Most of these deaths are preventable, but require resources, interventions, and policies that are guided by evidence \cite{benzigerGlobalBurdenDisease2016}. Thus, reliable counts and diagnoses of deaths provide decision makers with evidence to save lives and reduce premature deaths worldwide \cite{lawnMillionNeonatalDeaths2010,lassiCommunityBasedIntervention2015,liuExcessMortalityPersons2017,ewigCommunityacquiredPneumoniaEmergency2011}. However, most low-income countries do not have data on deaths or have registered less than half of the deaths in their country, with an even fewer 8\% of these registered deaths having a Cause of Death (COD) recorded \cite{worldhealthorganizationSCOREHealthData2021}. To fill this gap in death registrations, an alternative method known as Verbal Autopsy (VA) is used to collect data on deaths and determine their likely causes at scale \cite{desavignyIntegratingCommunitybasedVerbal2017,thomasVerbalAutopsyHealth2018,rampatigeSystematicReviewStatistics2014}, outside of traditional healthcare facilities where over half of deaths occur at home \cite{adairWhoDiesWhere2021}.

VA involves two major components: survey and COD assignment \cite{worldhealthorganizationVerbalAutopsyStandards2023,chandramohanEstimatingCausesDeath2021}. In the survey component, trained lay surveyors interview those familiar with the deceased (e.g. living spouse, children, family, friends) to gather information using standardized questionnaires and open narratives. In the COD assignment component, physicians evaluate information available from the questionnaires and open narratives to assign probable CODs. Although the survey component has been an effective alternative to collect mortality data at scale, the COD assignment component has been criticized to be expensive and difficult to reproduce due to reliance on physician assigned CODs \cite{mccormickProbabilisticCauseofDeathAssignment2016,morrisFactorsAssociatedPhysician2010}. As an alternative to physician assigned CODs, computer models, such as InterVA \cite{byassIntegratedApproachProcessing2019} and InSilicoVA \cite{mccormickProbabilisticCauseofDeathAssignment2016}, have recently been studied to automatically assign CODs with performances close to physicians at the population level, but poor performances at the individual level \cite{jhaAutomatedPhysicianAssignment2019,leitaoComparisonPhysiciancertifiedVerbal2014,desaiPerformanceFourComputercoded2014,tungaVerbalAutopsyModels2021}. These computer models often utilized data from the structured questionnaire, but often omit the free-text open narrative, which misses latent information, such as chronology or health-seeking behaviors, that may potentially help models perform better than using the questionnaire alone \cite{jebleeAutomaticallyDeterminingCause2019,blancoExtractingCauseDeath2021,kingQualityDiagnosticValue2016}.

Recently, Large Language Models (LLM), leveraging massive datasets and deep learning approaches, have made advances in performing a variety of Natural Language Processing (NLP) tasks using free-text, such as question answering, code generation, and even medical diagnosis \cite{changSurveyEvaluationLarge2023,lundChattingChatGPTHow2023,svyatkovskiyIntelliCodeComposeCode2020,hauptAIGeneratedMedicalAdvice2023}. On November 30, 2022, a widely-available LLM called ChatGPT was released by OpenAI with capabilities of answering natural language text inquiries using training data up to September 2021. ChatGPT-3 was based on several Generative Pre-trained Transformer (GPT) models between 2018 to 2020, namely GPT-1 to GPT-3, which had notable differences in training data sizes of 5 gigabytes to 45 terabytes from web sources that resulted in 117 million to 175 billion parameter models \cite{wuBriefOverviewChatGPT2023}. On March 14, 2023, ChatGPT-4 was released with human-level performance on various professional and academic exams and benchmarks that outperformed ChatGPT-3 \cite{openaiGPT4TechnicalReport2023a}. Given the limited usage of free-text open narratives in computer models for determining CODs, and recent advances in LLMs that leverage natural language text prompts, we conduct a case study with Sierra Leone deaths from VA in 2019 to 2022 to compare four models, ChatGPT-3.5, ChatGPT-4, InterVA-5, and InSilicoVA, for determining CODs.

@@

Initially, 11,920 records were collected from dual-coded Electronic Verbal Autopsy (EVA), where each record was randomly coded by two different physicians that assigned CODs as International Classification of Diseases Revision 10 (ICD-10) codes \cite{worldhealthorganizationICD10InternationalStatistical2011}. Physicians were able to assign CODs for 11,799 of the 11,920 records, where 121 of these records could not be assigned a COD due to missing or inadequate information (e.g. low quality narrative, data loss). To determine if two codes were in physician agreement, codes from two physicians per record were compared in the EVA system to determine if they agreed using Central Medical Evaluation Agreement 10 (CMEA-10) codes, which groups a range of similar ICD-10 codes together \cite{aleksandrowiczPerformanceCriteriaVerbal2014} (see Additional File 1). When codes were not in agreement, a record enters the reconciliation phase, where the two physicians were provided reasoning and codes from each other to: (1) keep their initial code (2) assign the other physician's code or (3) assign a new code. If codes are not in agreement after the reconciliation phase, a record enters the adjudication phase, where a third senior physician evaluates both physicians' reasoning and codes, and assigns a final code. The 11,799 physician coded records were further filtered for cases where both physicians agreed on the assigned codes (cases that were not reconciled or adjudicated), resulting in 6939 records.

@@

Four computer models were used to predict COD for each of the 6939 physician agreed records: ChatGPT-3.5 \cite{brownLanguageModelsAre2020}, ChatGPT-4 \cite{openaiGPT4TechnicalReport2023a}, InterVA-5 \cite{byassIntegratedApproachProcessing2019}, and InSilicoVA \cite{mccormickProbabilisticCauseofDeathAssignment2016}. Each model required pre-processing of the 11,799 physician agreed records into input data, and standardization of output COD codes from models for performance evaluation as not all models produced ICD-10 codes.

@@

\noindent For InterVA-5 and InSilicoVA, the standardized questionnaire data from the HEAL-SL EVA were first converted into 2016 World Health Organization (WHO) VA questionnaire revision 1.5.1 Open Data Kit (ODK) format \cite{nafundiODKCollectData2023}. The WHO revision 1.5.1 ODK data were further converted into OpenVA format \cite{liOpenVAToolkitVerbal2023} using the \verb|pyCrossVA| Python package \cite{thomasPycrossvaPrepareData}, and used as input for InterVA-5 and InSilicoVA. The input data were X generated prompts for ChatGPT-3.5 and ChatGPT-4, and X OpenVA formatted records for InterVA-5 and InSilicoVA.

>>>>

\title[Determining Causes of Death from Verbal Autopsy with ChatGPT: A Case Study of 6942 Deaths in Sierra Leone from 2019-2022]{Determining Causes of Death from Verbal Autopsy with ChatGPT: A Case Study of 6942 Deaths in Sierra Leone from 2019-2022}

@@

In 2019, 41 million people die prematurely from noncommunicable diseases every year, accounting for 74\% of all deaths globally \cite{worldhealthorganizationNonCommunicableDiseases2019}. Most of these deaths are preventable, but require adequate resource allocation, guided by evidence, to implement effective interventions and policies that target populations at risk \cite{benzigerGlobalBurdenDisease2016}. Thus, reliable counts and diagnoses of deaths provide decision makers with evidence to save lives and reduce premature deaths worldwide \cite{lawnMillionNeonatalDeaths2010,lassiCommunityBasedIntervention2015,liuExcessMortalityPersons2017,ewigCommunityacquiredPneumoniaEmergency2011}. However, most low-income countries do not have data on deaths or have registered less than half of the deaths in their country, with an even fewer 8\% of these registered deaths having a Cause of Death (COD) recorded \cite{worldhealthorganizationSCOREHealthData2021}. To fill this gap in death registrations, an alternative method known as Verbal Autopsy (VA) is used to collect data on deaths and determine their likely causes at scale \cite{desavignyIntegratingCommunitybasedVerbal2017,thomasVerbalAutopsyHealth2018,rampatigeSystematicReviewStatistics2014}, outside of traditional healthcare facilities where over half of deaths occur at home \cite{adairWhoDiesWhere2021}.

VA involves two major components: survey and COD assignment \cite{worldhealthorganizationVerbalAutopsyStandards2023,chandramohanEstimatingCausesDeath2021}. In the survey component, trained lay surveyors interview those familiar with the deceased (e.g. living spouse, children, family, friends) to gather information using standardized questionnaires and open narratives. In the COD assignment component, physicians evaluate information available from the questionnaires and open narratives to assign probable CODs. Although VA surveys have been an effective alternative to collect mortality data at scale (e.g. less than \$3 USD per house in India \cite{gomesNationwideMortalityStudies2017,jhaProspectiveStudyOne2005}), COD assignment has been criticized to be expensive and difficult to reproduce due to reliance on physician assignment \cite{mccormickProbabilisticCauseofDeathAssignment2016,morrisFactorsAssociatedPhysician2010}. As an alternative to physician assignment, computer models, such as InterVA \cite{byassIntegratedApproachProcessing2019} and InSilicoVA \cite{mccormickProbabilisticCauseofDeathAssignment2016}, have recently been studied to automatically assign CODs with performances close to physicians at the population level, but poor performances at the individual level \cite{jhaAutomatedPhysicianAssignment2019,leitaoComparisonPhysiciancertifiedVerbal2014,desaiPerformanceFourComputercoded2014,tungaVerbalAutopsyModels2021}. These computer models often utilized data from the structured questionnaire, but often omit the free-text open narrative, which misses latent information, such as chronology or health-seeking behaviors, that may potentially help models perform better than using the questionnaire alone \cite{jebleeAutomaticallyDeterminingCause2019,blancoExtractingCauseDeath2021,kingQualityDiagnosticValue2016}.

Recently, Large Language Models (LLM), leveraging massive datasets and deep learning approaches, have made advances in performing a variety of Natural Language Processing (NLP) tasks using free-text, such as question answering, code generation, and even medical diagnosis \cite{changSurveyEvaluationLarge2023,lundChattingChatGPTHow2023,svyatkovskiyIntelliCodeComposeCode2020,hauptAIGeneratedMedicalAdvice2023}. On November 30, 2022, a widely-available LLM called ChatGPT was released by OpenAI with capabilities of answering natural language text inquiries using training data up to September 2021. ChatGPT-3 was based on several Generative Pre-trained Transformer (GPT) models between 2018 to 2020, namely GPT-1 to GPT-3, which had notable differences in training data sizes of 5 gigabytes to 45 terabytes from web sources that resulted in 117 million to 175 billion parameter models \cite{wuBriefOverviewChatGPT2023}. On March 14, 2023, ChatGPT-4 was released with human-level performance on various professional and academic exams and benchmarks that outperformed ChatGPT-3 \cite{openaiGPT4TechnicalReport2023a}. Given the limited usage of free-text open narratives in computer models for determining CODs, and recent advances in LLMs that leverage natural language text prompts, we conduct a case study with Sierra Leone deaths from VA in 2019 to 2022 to compare the performances of four models, ChatGPT-3.5, ChatGPT-4, InterVA-5, and InSilicoVA, for determining CODs.

@@

Initially, 11,920 records were collected from dual-coded Electronic Verbal Autopsy (EVA), where each record was randomly coded by two different physicians that assigned CODs as International Classification of Diseases Revision 10 (ICD-10) codes \cite{worldhealthorganizationICD10InternationalStatistical2011}. Physicians were able to assign CODs for 11,820 of the 11,920 records, where 100 of these records could not be assigned a COD due to missing or inadequate information (e.g. low quality narrative, data loss). To determine if two codes were in physician agreement, codes from two physicians per record were compared in the EVA system to determine if they agreed using Central Medical Evaluation Agreement 10 (CMEA-10) codes, which groups a range of similar ICD-10 codes together \cite{aleksandrowiczPerformanceCriteriaVerbal2014} (see Additional File 1). When codes were not in agreement, a record enters the reconciliation phase, where the two physicians were provided reasoning and codes from each other to: (1) keep their initial code (2) assign the other physician's code or (3) assign a new code. If codes are not in agreement after the reconciliation phase, a record enters the adjudication phase, where a third senior physician evaluates both physicians' reasoning and codes, and assigns a final code. The 11,820 physician coded records were further filtered for records where both physicians agreed on the assigned codes (records that were not reconciled or adjudicated), resulting in 6942 physician agreed records. Since computer models were compared to physicians, there was more certainty that COD assignments agreed by both physicians were representative of physician assignment than when they disagreed \cite{barnettComparativeAccuracyDiagnosis2019,morrisFactorsAssociatedPhysician2010,hsiaoFactorsAssociatedPhysician2012}.

@@

Four computer models were used to predict COD for each of the 6942 physician agreed records: ChatGPT-3.5 \cite{brownLanguageModelsAre2020}, ChatGPT-4 \cite{openaiGPT4TechnicalReport2023a}, InterVA-5 \cite{byassIntegratedApproachProcessing2019}, and InSilicoVA \cite{mccormickProbabilisticCauseofDeathAssignment2016}. Each model required pre-processing of the 6942 physician agreed records into input data, and standardization of output COD codes from models for performance evaluation as not all models produced comparable codes across outputs.

@@

\noindent For InterVA-5 and InSilicoVA, the standardized questionnaire data from the HEAL-SL EVA were first converted into 2016 World Health Organization (WHO) VA questionnaire revision 1.5.1 Open Data Kit (ODK) format \cite{nafundiODKCollectData2023}. The WHO revision 1.5.1 ODK data were further converted into OpenVA format \cite{liOpenVAToolkitVerbal2023} using the \verb|pyCrossVA| Python package \cite{thomasPycrossvaPrepareData}, and used as input for InterVA-5 and InSilicoVA. The input data were 6939 generated prompts for ChatGPT-3.5 and ChatGPT-4, and X OpenVA formatted records for InterVA-5 and InSilicoVA.

### 2024-01-17 src/plots.Rmd
Checking counts

@@

# Models cases
models <- df %>% select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(models)) {
    m <- models[[mcol]]
    cat(paste0(
        str_replace_all(mcol, models_format), " Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}
```

>>>>

# Physician agreed cases
raw_physicians_agree <- raw_df %>%
    filter(is_agreed == TRUE) %>%
    pull(physician_cghr10)
cat(paste0(
    "Agreed Cases (",
    length(unique(na.omit(raw_physicians_agree))), " CODs): ",
    length(raw_physicians_agree),
    "\n"
))

@@

# Physician agreed cases
physicians_agree <- df %>%
    filter(is_agreed == TRUE) %>%
    pull(physician_cghr10)
cat(paste0(
    "Physician Agreed Coded Cases (",
    length(unique(na.omit(physicians_agree))), " CODs): ",
    length(physicians_agree) - sum(is.na(physicians_agree) | is.null(physicians_agree)),
    "\n"
))

# Models cases
models <- df %>% select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(models)) {
    m <- models[[mcol]]
    cat(paste0(
        str_replace_all(mcol, models_format), " Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}

# Models agreed cases
models_agree <- df %>%
    filter(is_agreed == TRUE) %>%
    select(ends_with("_cghr10"), -physician_cghr10)
for (mcol in colnames(models_agree)) {
    m <- models_agree[[mcol]]
    cat(paste0(
        str_replace_all(mcol, models_format), " Agreed Predicted Cases (", 
        length(unique(na.omit(m))), " CODs): ",
        length(m) - sum(is.na(m) | is.null(m)),
        "\n"
    ))
}
```

### 2024-01-17 src/preprocess.Rmd
Checking counts

# Read data
df <- list(
    wva2016_icd10 = read_csv(
        "../data/wva2016_icd10_v1.csv",
        col_types = cols(wva2016_code = col_double())
    ),
    icd10_cghr10 = read_csv("../data/icd10_cghr10_v1.csv"),
    physician = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_adult_v1.csv",
            col_select = all_of(phy_adult_cols)
        ) %>%
            mutate(round = 1, age = "adult") %>%
            rename(all_of(phy_adult_rename)),
        read_csv(
            "../tmp/healsl_rd2_adult_v1.csv",
            col_select = all_of(phy_adult_cols)
        ) %>%
            mutate(round = 2, age = "adult") %>%
            rename(all_of(phy_adult_rename)),
        read_csv(
            "../tmp/healsl_rd1_child_v1.csv",
            col_select = all_of(phy_cols)
        ) %>%
            mutate(round = 1, age = "child") %>%
            rename(all_of(phy_rename)),
        read_csv(
            "../tmp/healsl_rd2_child_v1.csv",
            col_select = all_of(phy_cols)
        ) %>%
            mutate(round = 2, age = "child") %>%
            rename(all_of(phy_rename)),
        read_csv(
            "../tmp/healsl_rd1_neo_v1.csv",
            col_select = all_of(phy_cols)
        ) %>%
            mutate(round = 1, age = "neo") %>%
            rename(all_of(phy_rename)),
        read_csv(
            "../tmp/healsl_rd2_neo_v1.csv",
            col_select = all_of(phy_cols)
        ) %>%
            mutate(round = 2, age = "neo") %>%
            rename(all_of(phy_rename))
    ),
    model_chatgpt3 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        )
    ) %>% rename(chatgpt3_icd10 = api_chat_icd),
    model_chatgpt4 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        )
    ) %>% rename(chatgpt4_icd10 = api_chat_icd),
    model_insilicova = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_insilicova_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_insilicova_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        )
    ) %>% rename(insilicova_wva2016 = cause1_wva),
    model_interva5 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_interva5_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_interva5_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        )
    ) %>% rename(interva5_wva2016 = cause1_wva)
)
```

@@

>>>>

# Read data
df <- list(
    wva2016_icd10 = read_csv(
        "../data/wva2016_icd10_v1.csv",
        col_types = cols(wva2016_code = col_double())
    ),
    icd10_cghr10 = read_csv("../data/icd10_cghr10_v1.csv"),
    physician = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_adult_v1.csv",
            col_select = all_of(phy_adult_cols)
        ) %>%
            mutate(round = 1, age = "adult") %>%
            rename(all_of(phy_adult_rename)),
        read_csv(
            "../tmp/healsl_rd2_adult_v1.csv",
            col_select = all_of(phy_adult_cols)
        ) %>%
            mutate(round = 2, age = "adult") %>%
            rename(all_of(phy_adult_rename)),
        read_csv(
            "../tmp/healsl_rd1_child_v1.csv",
            col_select = all_of(phy_cols)
        ) %>%
            mutate(round = 1, age = "child") %>%
            rename(all_of(phy_rename)),
        read_csv(
            "../tmp/healsl_rd2_child_v1.csv",
            col_select = all_of(phy_cols)
        ) %>%
            mutate(round = 2, age = "child") %>%
            rename(all_of(phy_rename)),
        read_csv(
            "../tmp/healsl_rd1_neo_v1.csv",
            col_select = all_of(phy_cols)
        ) %>%
            mutate(round = 1, age = "neo") %>%
            rename(all_of(phy_rename)),
        read_csv(
            "../tmp/healsl_rd2_neo_v1.csv",
            col_select = all_of(phy_cols)
        ) %>%
            mutate(round = 2, age = "neo") %>%
            rename(all_of(phy_rename))
    ),
    model_chatgpt3 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        )
    ) %>% rename(chatgpt3_icd10 = api_chat_icd),
    model_chatgpt4 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")
        )
    ) %>% rename(chatgpt4_icd10 = api_chat_icd),
    model_insilicova = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_insilicova_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_insilicova_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        )
    ) %>% rename(insilicova_wva2016 = cause1_wva),
    model_interva5 = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_rapid_interva5_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        ),
        read_csv(
            "../tmp/healsl_rd2_rapid_interva5_v1.csv",
            col_select = c("rowid", "round", "cause1_wva")
        )
    ) %>% rename(interva5_wva2016 = cause1_wva),
    narrative = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_adult_narrative_v1.csv",
            col_select = c("rowid", "summary")
        ),
        read_csv(
            "../tmp/healsl_rd1_child_narrative_v1.csv",
            col_select = c("rowid", "summary")
        ),
        read_csv(
            "../tmp/healsl_rd1_neo_narrative_v1.csv",
            col_select = c("rowid", "summary")
        ),
        read_csv(
            "../tmp/healsl_rd2_adult_narrative_v1.csv",
            col_select = c("rowid", "summary")
        ),
        read_csv(
            "../tmp/healsl_rd2_child_narrative_v1.csv",
            col_select = c("rowid", "summary")
        ),
        read_csv(
            "../tmp/healsl_rd2_neo_narrative_v1.csv",
            col_select = c("rowid", "summary")
        )
    ),
    who = bind_rows(
        read_csv(
            "../tmp/healsl_rd1_who_adult_v1.csv",
            col_select = c("rowid")
        ),
        read_csv(
            "../tmp/healsl_rd1_who_child_v1.csv",
            col_select = c("rowid")
        ),
        read_csv(
            "../tmp/healsl_rd1_who_neo_v1.csv",
            col_select = c("rowid")
        ),
        read_csv(
            "../tmp/healsl_rd2_who_adult_v1.csv",
            col_select = c("rowid")
        ),
        read_csv(
            "../tmp/healsl_rd2_who_child_v1.csv",
            col_select = c("rowid")
        ),
        read_csv(
            "../tmp/healsl_rd2_who_neo_v1.csv",
            col_select = c("rowid")
        )
    )
)
```

@@

## Checks

### Physician Coded Counts

Check physician coded record counts:

# Get icd10 counts
phy_icd10 <- out %>% filter(
    !is.na(physician_icd10) & !is.null(physician_icd10)
) %>% nrow
phy_icd10_agree <- out %>% filter(
     !is.na(physician_icd10) & !is.null(physician_icd10) & is_agreed == TRUE
) %>% nrow

# Get cghr10 counts
phy_cghr10 <- out %>% filter(
    !is.na(physician_cghr10) & !is.null(physician_cghr10)
) %>% nrow
phy_cghr10_agree <- out %>% filter(
     !is.na(physician_cghr10) & !is.null(physician_cghr10) & is_agreed == TRUE
) %>% nrow

# Print results
cat(paste0(
    "Physican ICD-10 Coded: ", phy_icd10,
    "\nPhysician ICD-10 Coded (Agree): ", phy_icd10_agree,
    "\nPhysican CGHR-10 Coded: ", phy_cghr10,
    "\nPhysician CGHR-10 Coded (Agree): ", phy_cghr10_agree
))
```

### ChatGPT-3.5 Counts

Check ChatGPT-3.5 Counts:

# Get phy coded records only
out_coded <- out %>% filter(
    !is.na(physician_icd10) & !is.null(physician_icd10)
)
out_coded_agree <- out_coded %>% filter(is_agreed == TRUE)

# Get chatgpt3 coded records
out_cgpt3 <- out_coded %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)
out_cgpt3_agree <- out_coded_agree %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)

# Get chatgpt3 coded records converted to cghr10
out_cgpt3_cghr10 <- out_cgpt3 %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)
out_cgpt3_cghr10_agree <- out_cgpt3_agree %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)

# Print results
cat(paste0(
    "ICD-10 Output\n-------------",
    "\nChatGPT-3.5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_cgpt3 %>% nrow,
    "\nChatGPT-3.5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt3_agree %>% nrow,
    "\n\nAfter Conversion to CGHR-10\n---------------------------",
    "\nChatGPT-3.5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt3_cghr10 %>% nrow,
    "\nChatGPT-3.5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt3_cghr10_agree %>% nrow
))
```

### ChatGPT-4 Counts

Check ChatGPT-4 Counts:

# Get phy coded records only
out_coded <- out %>% filter(
    !is.na(physician_icd10) & !is.null(physician_icd10)
)
out_coded_agree <- out_coded %>% filter(is_agreed == TRUE)

# Get chatgpt4 coded records
out_cgpt4 <- out_coded %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)
out_cgpt4_agree <- out_coded_agree %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)

# Get chatgpt4 coded records converted to cghr10
out_cgpt4_cghr10 <- out_cgpt4 %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)
out_cgpt4_cghr10_agree <- out_cgpt4_agree %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)

# Print results
cat(paste0(
    "ICD-10 Output\n-------------",
    "\nChatGPT-4 ICD-10 Coded (Phy. ICD-10 Coded): ", out_cgpt4 %>% nrow,
    "\nChatGPT-4 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt4_agree %>% nrow,
    "\n\nAfter Conversion to CGHR-10\n---------------------------",
    "\nChatGPT-4 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt4_cghr10 %>% nrow,
    "\nChatGPT-4 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt4_cghr10_agree %>% nrow
))
```

### Narrative Counts

Check narrative counts:

# Add narr
out_narr <- out %>% left_join(
    df$narrative,
    by = c("rowid" = "rowid"),
    suffix = c("", "")
) %>% filter(
    !is.na(summary)
)

# Display counts
narr_raw <- out_narr %>% nrow
narr_agree <- out_narr %>% filter(
    is_agreed == TRUE
) %>% nrow
narr_icd10 <- out_narr %>% filter(
    !is.na(physician_icd10)
) %>% nrow
narr_cghr10 <- out_narr %>% filter(
    !is.na(physician_cghr10)
) %>% nrow
narr_icd10_agree <- out_narr %>% filter(
    is_agreed == TRUE & !is.na(physician_icd10)
) %>% nrow
narr_cghr10_agree <- out_narr %>% filter(
    is_agreed == TRUE & !is.na(physician_cghr10)
) %>% nrow
cat(paste0(
    "Narratives: ", narr_raw,
    "\nNarratives (Agreed): ", narr_agree,
    "\nNarratives (Phy. ICD-10 Coded): ", narr_icd10,
    "\nNarratives (Phy. CGHR-10 Coded): ", narr_cghr10,
    "\nNarratives (Agreed, Phy. ICD-10 Coded): ", narr_icd10_agree,
    "\nNarratives (Agreed, Phy. CGHR-10 Coded): ", narr_cghr10_agree
))
```

### WHO Formatted Record Counts

Check WHO VA v1.5.1 formatted counts:

# Add who
out_who <- out %>% left_join(
    df$who %>% mutate(rowid_who = rowid),
    by = c("rowid" = "rowid"),
    suffix = c("", "")
) %>% filter(!is.na(rowid_who))

# Display counts
who_raw <- out_who %>% nrow
who_agree <- out_who %>% filter(
    is_agreed == TRUE
) %>% nrow
who_icd10 <- out_who %>% filter(
    !is.na(physician_icd10)
) %>% nrow
who_cghr10 <- out_who %>% filter(
    !is.na(physician_cghr10)
) %>% nrow
who_icd10_agree <- out_who %>% filter(
    is_agreed == TRUE & !is.na(physician_icd10)
) %>% nrow
who_cghr10_agree <- out_who %>% filter(
    is_agreed == TRUE & !is.na(physician_cghr10)
) %>% nrow
cat(paste0(
    "WHO Format Records: ", who_raw,
    "\nWHO Format Records (Agreed): ", who_agree,
    "\nWHO Format Records (Phy. ICD-10 Coded): ", narr_icd10,
    "\nWHO Format Records (Phy. CGHR-10 Coded): ", narr_cghr10,
    "\nWHO Format Records (Agreed, Phy. ICD-10 Coded): ", who_icd10_agree,
    "\nWHO Format Records (Agreed, Phy. CGHR-10 Coded): ", who_cghr10_agree
))
```
